Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
working on introduction

\section{Introduction}
\label{sec:introduction}

>>>>

\section{Introduction}
\label{sec:introduction}
  The Mississippi Emergency Management Administration (MSEMA) has hired our team to design evacuation routes for at-risk counties in the coastal regions of southern Mississippi. Given that this coastal area is a strong commercial center, the govermental authorities want to minimize the number of unnecessary evacuations. Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as possible. The reasons for this are two-fold. First, this ensures that local businesses can remain open for as long as possible. Second, this ensures that the forecasting reports at the time of the evacuation order are as accurate as possible. Therefore, our models seek to recommend an optimal evacuation plan as well as the latest possible time at which it is safe to enact this plan.
